SemanticPaint

### 2015-12-03 cv3d_seminar/paper.tex
crf

\usepackage{graphicx}   
% \usepackage{url}
% \usepackage{amsmath}

@@

\section{Dynamic Conditional Random Field}
\section{Efficient Mean-Field Inference}
\section{Streaming Random Forests}

  A random forest is an ensamble of classification or regression trees, whose outputs are combined to produce a result with lower variance \cite{murphy}. Each tree is typically trained only on a subset of the training data $S$ comprised of pairs $(i, l)$ where $i$ is a sample and $l$ its label.  Let $f(i; \theta) \in \{L, R\}$ denote the binary split function with learned parameters $\theta$, which specify a feature this node uses. The tree's output amounts to the probability distribution $P(c_i = l | i)$ stored at each node. Trees learn in a greedy way: for each node a split function is chosen from a distribution $\Theta$ of candidate split functions to maximize the information gain.

@@

@@

  \bibitem{murphy}
  murphy's ML

>>>>

\usepackage{graphicx}   
% \usepackage{url}
\usepackage{amsmath}

@@

\begin{figure}
 \center
 \includegraphics[width=0.75\textwidth]{figures/vop}
 \caption{Voxel Oriented Patch. Colours shown in RGB for illustration purposes.}
 \label{fig:vop}
\end{figure}

  Even the most powerful classifier will be useless if inappropriate features are supplied. Since speed is crucial, this paper contributes Voxel Oriented Patch (VOP) features, which can be computed efficiently from the TSDF volume representation (cf. figure \ref{fig:vop}. Let $V_i$ be a VOP and $\mathbf{n}^i$ the normal of voxel i. We create an image patch of dimensions $r \times r$  centered on voxel $i$ from the plane $(\mathbf{p} - \mathbf{p}_i) \cdot \mathbf(n)_i = 0$. The patch containes colour values stored in the TSDF on the plane in CIELab to mitigate illumination effects. Additionaly, $V_i$ stores distance to the nearest dominant horizontal surface. $r = 13$ with a resolution of $10\frac{mm}{pixel}$ is used. Rotation invariance is achieved exactly as in \cite{sift}. The patch is rotated according to the dominant gradient direction. It is computed by creating a histogram of gradient directions with 36 bins, where the directions are weighted by gradient magnitudes and a gaussian window centered at the voxel. Furthermore, a quadratic polynomial is fit to the three biggest values of the histogram, whose maximum is the final directiion.

\section{Streaming Random Forests}

  A random forest is an ensamble of classification or regression trees, whose outputs are combined to produce a result with lower variance \cite{online_forest}. Each tree is typically trained only on a subset of the training data $S$ comprised of pairs $(i, l)$ where $i$ is a sample and $l$ its label.  Let $f(i; \theta) \in \{L, R\}$ denote the binary split function with learned parameters $\theta$, which specify a feature this node uses. The tree's output amounts to the probability distribution $P(c_i = l | i)$ stored at each node. Trees learn in a greedy way: for each node a split function is chosen from a distribution $\Theta$ of candidate split functions to maximize the information gain.

@@

\section{Dynamic Conditional Random Field}
Conditional Random Field (CRF) [Lafferty et al.2001].

 Conditional Random Fields are often used for segmentation \cite{related_work}, where availability of all data is assumed. Here, the underlying model changes constantly (new frames, labels or different SRF prediction), which requires a novel inference alogorithm. The class of each voxel is modeled by a random variable $x_i$. The label distribution over the volume $\mathcal{V}$ factorizes into likelihood terms $\psi_i(x_i)$ and prior terms $\psi_{ij}(x_i, x_j)$. Let $\mathcal{E}_i$ be a neighbourhood of $v_i$, $\mathbf{D}_t $ volumetric data at time $t$ and $\mathbf{x}$ a vector of all $x_i$. The posterior distribution is given by

\begin{equation} \label{eq:posterior}
 P(\mathbf{x}|\mathbf{D}) = \prod_{i \in \mathcal{V}} \left( \psi_i(x_i) \prod_{j \in \mathcal{E}_i} \psi_{ij}(x_i, x_j) \right) 
\end{equation}

Neighbourhood of 6 cm is used. Negative log likelihood of eq. \ref{eq:posterior} defines the energy

\begin{equation} \label{eq:energy}
 E_t(\mathbf{x}) = \sum_{i \in \mathcal{V}} \left( \phi_i(x_i) + \sum_{j \in \mathcal{E}_i} \phi_{ij} (x_i, x_j) \right) + K
\end{equation}

Unary and pairwise potentials $\phi_i(x_i)$ and $\phi_{ij}(x_i, x_j)$ encode the cost of assigning label to $v_i$ and a cost of assuming different labels by voxels in a neighbourhood, respectively. They are constatly changing due to the chainging predictions of the random forest and user interaction.

Initially, all voxels are encouraged to take a background label by setting $\phi_i(l) = 0$ for background class and grater than zero otherwise. Later, these are replaced by the random forest predictions for each voxel and as a result of user interactions.

When the user touches an object, a set of touched voxels $\mathcal(H)_S$ is registered. Their unary potentials are set to $\phi_i(l) = \infty$ if their labels are different then the specified one, and zero if the same, thus imposing the labeling. If user labels a region more than once, the old labeling are simply overwritten.

To process the encircling action, the labeling is projected into the current frame. Next, a GMM is fittend with the foreground class taken as a convex hull of the encirvled region and background as the rest of the image. For every pixel in a bounding box around the user annotation the unary potential are updated as

\begin{equation}
 \phi_i(l) =
  \begin{cases}
    \log P_E(fg|\mathbf{a}_i)       & \quad \text{if } l = fg\\
    \log (1 - P_E(fg|\mathbf{a}_i))  & \quad \text{if } l = bg\\
  \end{cases}
\end{equation}

with $P_E(fg|\mathbf{a}_i)$ the probability of assuming the foreground label, which is a normalized likelihood $P_(\mathbf{a}_i|fg)$ from the GMM.

\begin{equation}
  P_E(fg|\mathbf{a}_i) = \frac{P_(\mathbf{a}_i|fg) }{P_(\mathbf{a}_i|fg) + P_(\mathbf{a}_i)|bg}
\end{equation}

Smoothness is achieved by the standard Potts model by assigning a disconuity cost $\phi_{ij}(x_i, x_j) = \lambda_{ij}$ if voxels have different labels and zero otherwise, with $\lambda_{ij}$ a function of difference in position, intensity and normal directions.

\section{Efficient Mean-Field Inference}

@@

  \bibitem{sift}
  L OWE , D. G. 1999. Object recognition from local scale-invariant features. In Proc. ICCV.
